The necessity of hypermedia RDF and an approach to achieve it

### 2012-03-01 eswc-2012/workshop2.tex
single endpoint?
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@137 43ef1190-90fd-4dd7-a769-d0121f02b80e

>>>>

\section{Required links}

As noted in \cite{sunsetonmvc}, AtomPub has a single service endpoint,
and you can navigate to what you need from there. This motivates the
first discussion topic of this paper:

\begin{question}
Is a single service endpoint enough for Linked Data?
\end{question}

We note that the distributed graph structure of the LOD Cloud makes
this awkward: For every new data source encountered in a graph
traversal, a new service endpoint must be queried. Moreover, it would
be awkward if fine-grained access controls for writing is being used
to record permissions for all resources in a single service
description. It seems likely that a few triples attached to each
information resource is better suited in most cases.
